Turbulence in compact to giant HII regions

### 2022-07-09 strucfunc_paper.tex
Added final paragraph for sec 5.1

@@

SUMMARISE COMPARISONS DESCRIBED IN APPENDIX.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.

>>>>

For most of our sources \(B\noise / \sigma^2\pos < 0.03 \) and the noise
has almost no effect on the structure function,
apart from at the very smallest separations,
resulting in a negligible influence on the other model parameters.
The exceptions are the Galactic regions Lagoon, Carina,
and especially the Extended Orion Nebula,
for which the noise is sufficiently large that the slope
of \(B\obs(r)\) is significantly shallower than
the inferred slope \(m\) of the true model \(B\model(r)\).
These sources also show the largest fluctuations
\(B\obs(r)\) around the smooth fit
at intermediate scales
(see in particular Figure~\ref{fig:strucfunc-fit-Galactic}d),
which is probably due to the relatively small number of spectra.

@@

Detailed comparisons with previous results are given
in section~\ref{sec:notes-individual-hii}.
In summary, we agree with previous studies in cases where there
is a good match in the exact area covered and in the angular resolution.
In other cases, large discrepancies are found,
which are probably to a combination of methodological differences
and real variations due to the inhomogeneity of the
velocity fluctuations on the largest scales.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin of error of our own results.
